---
title: "p8105_hw6_yg2625"
author: "Yue Gu"
date: "November 25, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
```{r, message = F}
library(tidyverse)
```

# Problem 1
## Import data
```{r, message = FALSE}
homi_raw = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
head(homi_raw, 10)
```

## Data manipulation
* Create a city_state variable, and a binary variable
* Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO; Tulsa, AL
* Modifiy victim_race to have categories white and non-white
* Transform victim_age as numeric
```{r, message = FALSE}
homi_create = 
  homi_raw %>% 
  mutate(city_state = paste(city, state, sep = ", "),
         solved = ifelse(disposition == "Closed without arrest" | disposition == "Open/No arrest", 0, 1)) %>% 
  filter(city_state != "Dallas, TX" , city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL") %>% 
  mutate(victim_race = ifelse(victim_race == "White", "white", "nonwhite"),
         victim_race = fct_relevel(victim_race, "white"),
         victim_age = as.numeric(victim_age))

class(homi_create$victim_age)
class(homi_create$victim_race)

```
As required, binary variable *solved* have value 0 if the case is unsolved, have value 1 if the case is solved, *victim_race* have categories white and non-white as factors and *victim_age* are numeric.

## Fit regression
* For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors
* Save the output of glm as an R object
```{r}
fit_log_balt = 
  homi_create %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())
  
```

* Apply the broom::tidy to this object
* Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed
```{r}
fit_log_balt %>% 
  broom::tidy() %>%
  mutate(OR = exp(estimate),
         OR_low = exp(estimate - qnorm(1-0.05/2)*std.error),
         OR_high = exp(estimate + qnorm(1-0.05/2)*std.error)) %>%
  select(term, estimate, OR, OR_low, OR_high) %>% 
  knitr::kable(digits = 3)
```

With the output, we could know the adjusted odds ratio for solving homicides comparing non-white victims to white victims is 0.441 keep all else fixed. And we are 95% confident that the adjusted odds ratio will fall in the range from 0.313 to 0.620.


* Run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims
```{r}
fit_log_all =
  homi_create %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenonwhite") %>%
  mutate(OR = exp(estimate),
         OR_low = exp(estimate - qnorm(1-0.05/2)*std.error),
         OR_high = exp(estimate + qnorm(1-0.05/2)*std.error)) %>% 
  select(-term, -std.error, -p.value, - statistic)

# show the first 10 outputs of the tidies model dataset
head(fit_log_all, 10)
```



